### 2016-04-04 writing/latex/coincidence.tex
Finish set coincidence section

    Now consider if the region is non-empty, by \LemmaRef{lem:incdec} and
    condition~\ref{prop:dom2:condc} of the proposition this region must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and move the points from the subsequence into
    the box southeast of the point. The other conditions allow this to be done
    without moving points into regions that were shaded.Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_1\}} \subseteq \av{\{\pi,m_2\}}\).

@@

In order to rigorously establish this coincidence we need to consider what would
happen if we were to choose a point in the box \((1,0)\) that we would like to shade.
In order to get a chance of getting the shading we want consider choosing the
rightmost point in the box.
This gives us the following mesh pattern.
\begin{equation*}
    \pattern{}{2,1,3}{0/3,2/0,2/1,3/0,3/1,3/2}
\end{equation*}
By application of the \PropositionRef{prop:dom1} we then achieve the following
mesh pattern
\begin{equation*}
    \pattern{2,3}{2,1,3}{0/3,2/0,2/1,3/0,3/1,3/2}
\end{equation*}
If we look at the highlighted points we see that the subpattern is an occurrence
of the mesh pattern that we originally desired. This gives rise to the following
rule:

\begin{proposition}[Third Dominating Pattern Rule]
    \label{prop:dom3}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\)\footnote{The
    permutation \(\pi\) may be the empty permutation}, the sets
    \(\av{\{\pi,m_1\}}\) and \(\av{\{\pi,m_2\}}\) are coincident if
    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item \(\addp[D]{\mperm{\sigma}{R_1}}{(a,b)}\) is coincident with a
            mesh pattern containing an occurrence of \(\mperm{\sigma}{R_2}\).
    \end{enumerate}
\end{proposition}
\begin{proof}
    We need to prove that \(\av{\{\pi,m_1\}} = \av{\{\pi,m_2\}}\).

@@

    Now consider a permutation in \(\av{\pi}\)
\end{proof}

@@

The patterns \fxnote{Is this dom3?}
\begin{equation*}
    \pattern{}{1,2}{0/0, 0/2, 1/1, 1/2, 2/1} \text { and } \pattern{}{1,2}{0/0, 0/1, 0/2, 1/1, 1/2, 2/1}
\end{equation*}
are equivalent in \(\av{\perm{3,2,1}}\). (There are 3 symmetries of these
patterns that are also equivalent to each other by the same reasoning.)

@@

The other reasoning applies to the patterns
\begin{equation*}
    \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
\end{equation*}
which are coincident by expermentation.

In order to explain this we need to consider the middle box, and
any points that it may contain. If the box is empty, then the coincidence
is trivially true. Hence, consider if there is a point in the box. This
gives us a mesh pattern
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=0.5, baseline=(current bounding box.center)]
        \modpattern[4]{}{1,2,3}{0/1,0/2,0/3,3/0,3/1,3/2}
        \draw (1.5,3.5) node {\(A\)};
        \draw (2.5,0.5) node {\(B\)};
    \end{tikzpicture}}
\end{equation*}

Where at most one of \(A\) or \(B\) contains an increasing subsequence.
If both are empty we can \emph{a posteriori} make our point in the center
box be either the leftmost, or the rightmost. Now consider if the box \(A\)
were to contain any points, we now know that the box labelled \(B\) contains
no points and can be shaded. By previously established rules we can also obtain
other shadings, leading to the following mesh pattern.
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=0.5, baseline=(current bounding box.center)]
        \modpattern[4]{}{1,2,3}{0/1,0/2,0/3,3/0,3/1,3/2}
        \filldraw (1.5,3.5) circle (4 pt);
        \shadeboxes{2/0,2/1}
    \end{tikzpicture}}
\end{equation*}
Now we can \emph{a posteriori} say that our point in the center box was the
rightmost, giving
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=0.5, baseline=(current bounding box.center)]
        \modpattern[4]{1,2}{1,2,3}{0/1,0/2,0/3,3/0,3/1,3/2}
        \filldraw (1.5,3.5) circle (4 pt);
        \shadeboxes{1/1,1/2,2/0,2/1}
    \end{tikzpicture}}
\end{equation*}
This gives shading that when we choose the highlighted points we
get an occurrence of the required mesh pattern, and as such the
two patterns are coincident.

This argument applies to another pair of classes. Therefore in
total in \(\av{\perm{3,2,1}, \mperm{1,2}{R}}\) there are \(213\) equivalence
classes.

>>>>

    Now consider if the region is non-empty, by \LemmaRef{lem:incdec} and
    condition~\ref{prop:dom2:condc} of the proposition this region must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and the points from the subsequence are now in
    the box southeast of the point. The other conditions allow this to be done
    without points being present in regions that were shaded. Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\).

@@

In order to rigorously establish this coincidence we need to consider what would
happen if we were to choose a point in the box \((1,0)\) that we would like to shade.
In order to get a chance of getting the shading we want consider choosing the
rightmost point in the box.
This gives us the following mesh pattern.
\begin{equation*}
    \pattern{}{2,1,3}{0/3,2/0,2/1,3/0,3/1,3/2}
\end{equation*}
By application of the \PropositionRef{prop:dom1} we then achieve the following
mesh pattern
\begin{equation*}
    \pattern{2,3}{2,1,3}{0/3,1/3,2/0,2/1,3/0,3/1,3/2}
\end{equation*}
If we look at the highlighted points we see that the subpattern is an occurrence
of the mesh pattern that we originally desired. This gives rise to the following
rule:

\begin{proposition}[Third Dominating Pattern Rule]
    \label{prop:dom3}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\)\footnote{The
    permutation \(\pi\) may be the empty permutation}, the sets
    \(\av{\{\pi,m_1\}}\) and \(\av{\{\pi,m_2\}}\) are coincident if
    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item\label{prop:dom3:condocc} \(\addp[D]{\mperm{\sigma}{R_1}}{(a,b)}\)
            is coincident with a mesh pattern containing an occurrence of
            \(\mperm{\sigma}{R_2}\).
    \end{enumerate}
\end{proposition}
\begin{proof}
    We need to prove that \(\av{\{\pi,m_1\}} = \av{\{\pi,m_2\}}\).

@@

    Now consider a permutation \(\varrho\) in \(\av{\pi}\) that contains an
    occurrence of \(m_1\). If the region corresponding to the box \((a,b)\)
    is empty then we have an occurrence of \(m_2\). If the region is non-empty
    then by condition~\ref{prop:dom3:condocc}  of the proposition there exists
    a direction such that there exists an occurrence of a mesh pattern of
    length one longer than \(m_1\) in this position. This mesh pattern is
    coincident with another mesh pattern. This mesh pattern contains an
    occurrence of \(m_2\) so every occurrence of \(m_1\) is also an occurrence
    of \(m_2\).  Thus \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\) and the
    two patterns are coincident.
\end{proof}

@@

The patterns
\begin{equation*}
    \pattern{}{1,2}{0/0, 0/2, 1/1, 1/2, 2/1} \text { and } \pattern{}{1,2}{0/0, 0/1, 0/2, 1/1, 1/2, 2/1}
\end{equation*}
are equivalent in \(\av{\perm{3,2,1}}\). (There are 3 symmetries of these
patterns that are also equivalent to each other by the same reasoning.)

@@

The other reasoning applies to the patterns
\begin{equation*}
    m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } m_2 = \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
\end{equation*}
which are coincident by expermentation.

In order to prove this coincidence we will proceed by mathematical
induction on the number of points in the middle box we call this number \(n\).
\begin{description}
    \item [Base Case \((n=0)\):] The base case hold since we can freely shade the
        box if it contains no points.
    \item [Inductive Hypothesis \((n=k)\):] Suppose that the we can find an occurrence
        of the second pattern if we have an occurrence of the first with \(k\) points
        in the middle box.
    \item [Inductive Step \((n=k+1)\)] Suppose that we have \((k+1)\) points in
        the middle box. Choose the bottom most point in the middle box, this gives a
        mesh pattern equivalent to
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{}{1,2,3}{0/1,0/2,0/3,1/1,2/1,3/0,3/1,3/2}
            \draw (2.5,0.5) node {\(X\)};
        \end{tikzpicture}
    \end{equation*}
        Now we need to consider the box labelled \(X\) if this box is empty then
        we have an occurrence of \(m_2\) and are done. If this box contains
        any points then we gain some extra shading on the mesh pattern
        due to the dominating pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{2,3}{1,2,3}{0/1,0/2,0/3,1/1,1/2,1/3,2/1,3/0,3/1,3/2}
            \filldraw (2.5,0.5) circle (4 pt);
        \end{tikzpicture}
    \end{equation*}
        The two highlighted points form an occurrence of \(m_1\) with \(k\)
        points in the middle box, and thus by the Inductive Hypothesis we
        are done.
\end{description}
By induction we have that every occurrence of \(m_1\) is an occurrence of \(m_2\)
and by \NoteRef{not:downcmesh} every occurrence of \(m_2\) is an occurrence of
\(m_1\) so the two patterns are coincident.
This argument applies to another two pairs of classes. Therefore in
total in \(\av{\perm{3,2,1}, \mperm{1,2}{R}}\) there are \(213\) equivalence
classes.
